Weather Data Integration and Assimilation System\\

### 2020-02-16 Paper.tex
change API with texttt
cref tables and auto-scaling

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%We describe our experience with implementing an extendable open source Weather Data Integration and Assimilation System, which is known as \acrshort{wdias}. It uses the modern architecture pattern such as microservice in order to achieve the scalability, rather using monolithic architecture or client service architecture. It provides a modular approach to integration data from different sources and export into different formats. Also the inbuilt extension module system allow users to add new features. The open source tools that are using for \acrshort{wdias} allows to run on Cloud Computing platforms without much hassle with the auto scaling feature allow to run \acrshort{wdias} from 1 CPU node to nodes with few hundred CPUs. The paper describes the initial design goals, evolve over few architectures to get desired performance, and explains how the system in way to achieve scalability. Later we analyse the performance test observations with the performance metrics.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}}
\caption{Performance test 15min data enabled auto scaling - response latencies against server hits over the elapsed time.}
\label{fi:test_obs_auto_all_15_min_latency_vs_hits}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}}
\caption{Performance test 15min data enabled auto scaling - transnational throughput vs number of active threads.}
\label{fi:test_obs_auto_all_15_min_throughput_vs_threads}
\end{figure}

\subsection{Discussion}
\paragraph{Latency}
The latency for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number. But for each test run the latency kept constant over the time.
During the \cref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \cref{subse:obs_test_plan_all_15min}. Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

@@

\paragraph{Auto Scaling}
The \acrshort{wdias} supports auto scaling by out of the box with \acrshort{k8s}. Services can configure with maximum number of pods in order to avoid over resource usage. When there is not much workload on the system, system cool down to less pods in order to save more resources. When there is any issue with a pod, \acrshort{k8s} auto schedule another pod and remove the unhealthy pod. Also it allows to update the system without any down time with rollback updates.

\paragraph{Risk of Unable to Process Data}
During the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data. If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads. Also while configure for the auto scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%. Such configuration with always spawn new pods to handle double of current peak load.

@@

\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of \cref{subse:test_sys_config}.
During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%We describe our experience with implementing an extendable open source Weather Data Integration and Assimilation System, which is known as \acrshort{wdias}. It uses the modern architecture pattern such as microservice in order to achieve the scalability, rather using monolithic architecture or client service architecture. It provides a modular approach to integration data from different sources and export into different formats. Also the inbuilt extension module system allow users to add new features. The open source tools that are using for \acrshort{wdias} allows to run on Cloud Computing platforms without much hassle with the auto-scaling feature allow to run \acrshort{wdias} from 1 CPU node to nodes with few hundred CPUs. The paper describes the initial design goals, evolve over few architectures to get desired performance, and explains how the system in way to achieve scalability. Later we analyse the performance test observations with the performance metrics.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}}
\caption{Performance test 15min data enabled auto-scaling - response latencies against server hits over the elapsed time.}
\label{fi:test_obs_auto_all_15_min_latency_vs_hits}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}}
\caption{Performance test 15min data enabled auto-scaling - transnational throughput vs number of active threads.}
\label{fi:test_obs_auto_all_15_min_throughput_vs_threads}
\end{figure}

\subsection{Discussion}
\paragraph{Latency}
The latency for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throughout the whole test plan with a smaller number. But for each test run the latency kept constant over the time.
During the \cref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \cref{subse:obs_test_plan_all_15min}. Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

@@

\paragraph{Auto Scaling}
The \acrshort{wdias} supports auto-scaling by out of the box with \acrshort{k8s}. Services can configure with maximum number of pods in order to avoid over resource usage. When there is not much workload on the system, system cool down to less pods in order to save more resources. When there is any issue with a pod, \acrshort{k8s} auto schedule another pod and remove the unhealthy pod. Also it allows to update the system without any down time with rollback updates.

\paragraph{Risk of Unable to Process Data}
During the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data. If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads. Also while configure for the auto-scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%. Such configuration with always spawn new pods to handle double of current peak load.

@@

\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of \cref{subse:test_sys_config}.
During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.

### 2020-02-16 results/sec_1-test_plan.tex
cref tables and auto-scaling

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{Test Scenarios}}
\label{subse:test_plan_flow}
Following are the test cases which are planned to performance test cases;
\begin{enumerate}
    \item Test Setup to create timeseries in 1hr, 30min and 15min intervals and create metadata of the timeseries
    % \item Extensions
    % \begin{itemize}
    %     \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
    %     \item Plan for the 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
    %     \item Do with Import Timeseries with error data which will go through extensions.
    % \end{itemize}
    \item Import + Extension + Export + Timeseries Queries
    \begin{itemize}
        \item Plan for 30 minutes of the test run with the request size of 1hr (60min) data.
        \item Plan for 30 minutes of the test run with the request size of 30min data.
        \item Plan for 30 minutes of the test run with the request size of 15min data.
        \item Plan for 30 minutes of the test run with the request size of 15min data with Auto Scaling.
        \item All test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the Auto Scaling. (total of 2 hours)
    \end{itemize}
    \item Query
    \begin{itemize}
        \item Query Timeseries
        \item Plan for the 5 minutes of test run. (total 1/12 hours)
    \end{itemize}
\end{enumerate}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{Test Scenarios}}
\label{subse:test_plan_flow}
Following are the test cases which are planned to performance test cases;
\begin{enumerate}
    \item Test Setup to create timeseries in 1hr, 30min and 15min intervals and create metadata of the timeseries
    % \item Extensions
    % \begin{itemize}
    %     \item Create Extensions for /Aggregation\_Accumulative, /Interpolation Linear, /Validation Missing Values (OnChange and OnTime)
    %     \item Plan for the 15 minutes of test run with the request size of 15min data. (total 0.25 hours)
    %     \item Do with Import Timeseries with error data which will go through extensions.
    % \end{itemize}
    \item Import + Extension + Export + Timeseries Queries
    \begin{itemize}
        \item Plan for 30 minutes of the test run with the request size of 1hr (60min) data.
        \item Plan for 30 minutes of the test run with the request size of 30min data.
        \item Plan for 30 minutes of the test run with the request size of 15min data.
        \item Plan for 30 minutes of the test run with the request size of 15min data with auto-scaling.
        \item All test plan run against 60min, 30min and 15min request size of data. Another test plan runs with enabling the auto-scaling. (total of 2 hours)
    \end{itemize}
    \item Query
    \begin{itemize}
        \item Query Timeseries
        \item Plan for the 5 minutes of test run. (total 1/12 hours)
    \end{itemize}
\end{enumerate}

### 2020-02-16 results/sec_3-observations.tex
cref tables and auto-scaling

Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size. Then another performance test with enabling Auto Scaling as explained in \cref{subse:test_plan_metrics} for high resource utilized microservice.

@@

\cref{fi:test_obs_all_15m_response_vs_threads} shows the response time against the number of active threads for 15min data. As the graph shows, the response time kept the same while increasing the number of active threads against each test case. When the number of active threads increased more than 140, the \ref{fi:test_obs_all_15m_response_vs_threads} show uncertainty in the inserting and retrieving all data types. The latency of insert and retrieve Grid timeseries data goes up compared to \ref{fi:test_obs_all_30m_response_vs_threads}.
With higher request size, it becomes to notice the latency also increase by a small factor when the number of active thread increased. This can notice on with insert and retrieval of Grid timeseries data.

@@

\ref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
The formula for total server transaction throughput is \(<active threads> * 1 second / <1  thread response time>\) \cite{JMeterPluginsTransactionPlugin}. It shows the statistical maximum possible number of transactions based on the number of users accessing the application.
By combining the \ref{fi:test_obs_all_15m_latency}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_percentiles.png}
    \caption{Load testing with 15 minutes data - Response times Percentiles}
    \label{fi:test_obs_all_15m_latency_percentile}
\end{figure}
\ref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \cref{tab:obs_all_15_min_summary} latency up to 90\% percentile. With higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.

@@

This \cref{subse:obs_test_plan_all_auto_15min} discussed the test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the \cref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_15min} processed samples.
Other than that, this test plan runs with enabling \acrshort{k8s} Auto-scaling for the high resource utilized microservice as explained in \cref{subse:test_plan_metrics}. With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory. During this test plan, \acrshort{wdias} start with the auto scaling enabled for import-ascii-grid-upload microservice. Since adapter-grid is a consistent service for storing netCDF files, it is not possible to auto scale, since \acrshort{eks} does not support multiple reads writes support volumes \cite{LinuxFoundationPersistentKubernetes}.

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 15min data while enabled \acrshort{k8s} Auto Scaling}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71693 & 7 & 5 & 1608 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 77 & 233 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 63 & 1694 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
Query: Location & 71704 & 1 & 0 & 203 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\label{tab:obs_all_auto_15_min_summary}
\end{table}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data with enabled auto scaling - Latency against server hits}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\ref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for \acrshort{k8s}.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
When compared to \ref{fi:test_obs_all_15m_latency}, throughout the test period, the latency spikes become less.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data with enabled auto scaling - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_auto_15m_throughtput}
\end{figure}

\ref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against number of active threads.
When compared to \ref{fi:test_obs_all_15m_throughtput}, the estimated throughput with a higher number of active threads become stable at the graph. This means enabling auto-scaling also improves the throughput with a higher number of active users as well.

The following charts show the resource usage while running the all test plan while enabling the auto-scaling.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
    \caption{Load testing with auto scaling resource usage of import and export modules.}
    \label{fi:obs_all_auto_15m_import_export_res}
\end{figure}

\ref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and Memory usage for import timeseries modules and export timeseries modules. The CPU usage is shown with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the Memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes}. Noticeable, the import-ascii-grid-upload microservice used around 10 CPUs at the peak time while using 3.6 Gb of Memory. Another important fact is, after the test cases finished, the \acrshort{wdias} cool down the system via \acrshort{k8s} auto-scaling and release the resources. This clearly shows the elasticity of the \acrshort{wdias} according to the workload.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
    \caption{Load testing with auto scaling import ascii grid number of pods over time.}
    \label{fi:obs_all_auto_15m_import_grid_pod}
\end{figure}
\ref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled over time. The auto scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%. And the pods scheduled with 1 CPU requested, and limit with 2 CPUs per pod.
As the graph shows, 3 pods scheduled at the initial as per the configuration of the helm chart. While increasing the workload, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization. After \acrshort{k8s} spawn 10 maximum pods, it stop spawning new pods. But the pods were able to perform with vertical scaling, since those are not hit the CPU limit of 2.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
    \caption{Load testing with auto scaling resource usage of database adapters.}
    \label{fi:obs_all_auto_15m_adapter_dbs_res}
\end{figure}
\ref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
    \caption{Load testing query test over 5 minutes - Response Latency over Time}
    \label{fi:test_obs_query_5m_response_latency}
\end{figure}
\ref{fi:test_obs_query_5m_response_latency} shows the response latency over time for the query test plan. When the number of request get higher, the latency also get increased. That means adapter-query is not very much scalable with the current configurations.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_response_times_vs_threads.png}
    \caption{Load testing query test over 5 minutes - Response Latency Times vs Threads}
    \label{fi:test_obs_query_5m_response_times_vs_threads}
\end{figure}
\ref{fi:test_obs_query_5m_response_times_vs_threads} shows the response latency against number of active threads for the query test plan. When the number of server hits get higher, the latency also get increased. That means adapter-query is not very much scalable with the current configurations.

>>>>

Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size. Then another performance test with enabling auto-scaling as explained in \cref{subse:test_plan_metrics} for high resource utilized microservice.

@@

\cref{fi:test_obs_all_15m_response_vs_threads} shows the response time against the number of active threads for 15min data. As the graph shows, the response time kept the same while increasing the number of active threads against each test case. When the number of active threads increased more than 140, the \cref{fi:test_obs_all_15m_response_vs_threads} show uncertainty in the inserting and retrieving all data types. The latency of insert and retrieve Grid timeseries data goes up compared to \cref{fi:test_obs_all_30m_response_vs_threads}.
With higher request size, it becomes to notice the latency also increase by a small factor when the number of active thread increased. This can notice on with insert and retrieval of Grid timeseries data.

@@

\cref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
The formula for total server transaction throughput is \(<active threads> * 1 second / <1  thread response time>\) \cite{JMeterPluginsTransactionPlugin}. It shows the statistical maximum possible number of transactions based on the number of users accessing the application.
By combining the \cref{fi:test_obs_all_15m_latency}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_percentiles.png}
    \caption{Load testing with 15 minutes data - Response times Percentiles}
    \label{fi:test_obs_all_15m_latency_percentile}
\end{figure}
\cref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \cref{tab:obs_all_15_min_summary} latency up to 90\% percentile. With higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.

@@

This \cref{subse:obs_test_plan_all_auto_15min} discussed the test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the \cref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_15min} processed samples.
Other than that, this test plan runs with enabling \acrshort{k8s} Auto-scaling for the high resource utilized microservice as explained in \cref{subse:test_plan_metrics}. With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory. During this test plan, \acrshort{wdias} start with the auto-scaling enabled for import-ascii-grid-upload microservice. Since adapter-grid is a consistent service for storing netCDF files, it is not possible to auto scale, since \acrshort{eks} does not support multiple reads writes support volumes \cite{LinuxFoundationPersistentKubernetes}.

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 15min data while enabled \acrshort{k8s} auto-scaling}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71693 & 7 & 5 & 1608 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 77 & 233 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 63 & 1694 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
Query: Location & 71704 & 1 & 0 & 203 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\label{tab:obs_all_auto_15_min_summary}
\end{table}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data with enabled auto-scaling - Latency against server hits}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for \acrshort{k8s}.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
When compared to \cref{fi:test_obs_all_15m_latency}, throughout the test period, the latency spikes become less.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data with enabled auto-scaling - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_auto_15m_throughtput}
\end{figure}

\cref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against number of active threads.
When compared to \cref{fi:test_obs_all_15m_throughtput}, the estimated throughput with a higher number of active threads become stable at the graph. This means enabling auto-scaling also improves the throughput with a higher number of active users as well.

The following charts show the resource usage while running the all test plan while enabling the auto-scaling.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
    \caption{Load testing with auto-scaling resource usage of import and export modules.}
    \label{fi:obs_all_auto_15m_import_export_res}
\end{figure}

\cref{fi:obs_all_auto_15m_import_export_res} shows the CPU usage and Memory usage for import timeseries modules and export timeseries modules. The CPU usage is shown with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the Memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes}. Noticeable, the import-ascii-grid-upload microservice used around 10 CPUs at the peak time while using 3.6 Gb of Memory. Another important fact is, after the test cases finished, the \acrshort{wdias} cool down the system via \acrshort{k8s} auto-scaling and release the resources. This clearly shows the elasticity of the \acrshort{wdias} according to the workload.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
    \caption{Load testing with auto-scaling import ascii grid number of pods over time.}
    \label{fi:obs_all_auto_15m_import_grid_pod}
\end{figure}
\cref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled over time. The auto-scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%. And the pods scheduled with 1 CPU requested, and limit with 2 CPUs per pod.
As the graph shows, 3 pods scheduled at the initial as per the configuration of the helm chart. While increasing the workload, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization. After \acrshort{k8s} spawn 10 maximum pods, it stop spawning new pods. But the pods were able to perform with vertical scaling, since those are not hit the CPU limit of 2.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
    \caption{Load testing with auto-scaling resource usage of database adapters.}
    \label{fi:obs_all_auto_15m_adapter_dbs_res}
\end{figure}
\cref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
    \caption{Load testing query test over 5 minutes - Response Latency over Time}
    \label{fi:test_obs_query_5m_response_latency}
\end{figure}
\cref{fi:test_obs_query_5m_response_latency} shows the response latency over time for the query test plan. When the number of request get higher, the latency also get increased. That means adapter-query is not very much scalable with the current configurations.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_response_times_vs_threads.png}
    \caption{Load testing query test over 5 minutes - Response Latency Times vs Threads}
    \label{fi:test_obs_query_5m_response_times_vs_threads}
\end{figure}
\cref{fi:test_obs_query_5m_response_times_vs_threads} shows the response latency against number of active threads for the query test plan. When the number of server hits get higher, the latency also get increased. That means adapter-query is not very much scalable with the current configurations.

### 2020-02-16 results/sec_4-discussion.tex
change API with texttt
Fixed:  workload
cref tables and auto-scaling

\section{Performance Metrics Analysis}

@@

The \emph{Latency} for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number. But for each test run the latency kept constant over the time.
During the \cref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \cref{subse:obs_test_plan_all_15min}. Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

@@

\emph{Risk of unable to process data} during the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data. If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads. Also while configure for the auto scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%. Such configuration with always spawn new pods to handle double of current peak load.

>>>>

\section{Performance Metrics Analysis}
\label{se:discussion}

@@

The \emph{Latency} for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throughout the whole test plan with a smaller number. But for each test run the latency kept constant over the time.
During the \cref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \cref{subse:obs_test_plan_all_15min}. Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

@@

\emph{Risk of unable to process data} during the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data. If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads. Also while configure for the auto-scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%. Such configuration with always spawn new pods to handle double of current peak load.

### 2020-02-16 summary/sec_1-conclusions.tex
cref tables and auto-scaling

Load testing of \acrshort{wdias} was perform using the \acrshort{jmeter} tool's distributed testing capabilities. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of \cref{subse:test_sys_config}. Based on the observations, the system were able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero. Also, while increasing the request size from 24 to 96 data points per scalar and vector timeseries, and number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to perform same while keeping the latency constant without any significant change. During the performance test plans, the system were able to provide increase the throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with auto scaling configurations. 
The results of \acrshort{wdias} shows that the system can run from 1 CPU node to nodes with few hundred CPUs.

>>>>

Load testing of \acrshort{wdias} was perform using the \acrshort{jmeter} tool's distributed testing capabilities. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of \cref{subse:test_sys_config}. Based on the observations, the system were able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero. Also, while increasing the request size from 24 to 96 data points per scalar and vector timeseries, and number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to perform same while keeping the latency constant without any significant change. During the performance test plans, the system were able to provide increase the throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with auto-scaling configurations. 
The results of \acrshort{wdias} shows that the system can run from 1 CPU node to nodes with few hundred CPUs.
